---
title       : 2. Meetup of the Berlin R Users Group
subtitle    : 2015-07-23 @ Microsoft Berlin Digital Eatery (Berlin, DE)
author      : Konstantin Greger
job         : 
logo        : Rlogo.png
biglogo     : Rlogo.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Schedule for today

Time|What's happening
-------|-------
19:00|doors open
19:15|Konstantin Greger ([@kogreger](https://twitter.com/kogreger)): "Welcome address and brief introduction"
19:20|Berry Boessenkool ([@berryboessenkoo](https://twitter.com/berryboessenkoo)): TBA
19:35|Rick Scavetta ([@Rick_Scavetta](https://twitter.com/rick_scavetta)): "Some New Data Vis Tools in R - visR! 2015""
19:50|Andrew Dolman: "New R Engines and Interpreters""
20:05|Konstantin Greger ([@kogreger](https://twitter.com/kogreger)): "Spatial Analysis in R"
20:05|Michael Rustler: "Creating a Crowd Based Central Knowledge Hub for Reproducible Research with R"
afterwards|socializing & networking
22:00|doors close

```{r initialize, echo = FALSE, message = FALSE, cache = FALSE}
# initialize libraries
suppressMessages(library(slidify))
suppressMessages(library(googlesheets))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))
suppressMessages(library(jpeg))
suppressMessages(library(dplyr))
suppressMessages(library(png))
suppressMessages(library(readr))
suppressMessages(library(reshape2))
suppressMessages(library(stringr))


# survey data from Google Sheet
## download data
surveyRaw <- gs_key("1fpPQSD1hV15Rh5SiyyBhwePIBK0hIGWzvVyWGwvMiiM")
survey <- surveyRaw %>% 
    gs_read(ws = "Form Responses 1")
## extract original questions and make pretty
questions <- names(survey) %>% 
    gsub("\\.", " ", .) %>% 
    gsub("I ([dm].)", "I'\\1", .) %>% 
    gsub("    ", " ...", .)
## reorder questions
## (Google Forms remembers the order the questions were created...)
qOrder <- c(1, 2, 3, 16, 8, 9, 10, 11, 24, 25, 
            20, 21, 22, 14, 15, 18, 4, 5, 6, 23, 
            7, 12, 13, 17, 19)
survey <- survey %>% 
    select(qOrder)
questions <- questions[qOrder]
## generate generic question labels Q01..Q25
names(survey) <- c(paste0(rep("Q", 25), 
                        sprintf("%02d", seq(1:25))))


# group stats from meetup.com
# (currently the user stats are not downloadable automatically)
# (also, while the file has an .XLS extension it's actually a horribly 
#  formatted .TSV!)
## download and preprocess
memberStats <- read_tsv("../Berlin_R_Users_Group_Total_and_Active_Members.xls", 
                  col_types = "ccc") %>% 
    rename(date = `Date `, 
           total = `Total Members `, 
           active = `Active Members`) %>% 
    mutate(date = str_trim(date), 
           date = as.Date(date, format = "%Y-%m-%d"), 
           total = str_trim(total), 
           total = as.integer(total), 
           active = as.integer(active)) %>% 
    filter(!is.na(date))
## extract highest membership data
maxMembers <- data.frame(
    date = memberStats$date[which.max(memberStats$total)], 
    members = c(max(memberStats$total))
)
## combine total and active membership data
memberStats <- melt(memberStats, 
                    id.vars = "date", 
                    value.name = "members", 
                    variable.name = "status")
## create milestones
milestones <- data.frame(
    date = as.Date(c("2015-01-05", 
                     "2015-05-04", 
                     "2015-05-10", 
                     "2015-05-29", 
                     "2015-06-24", 
                     "2015-06-30"), 
                   format = "%Y-%m-%d"), 
    event = c("group founded", 
              "leadership changed", 
              "reboot announced\n@BerlinRUG started", 
              "first meetup scheduled", 
              "1. Meetup", 
              "second meetup scheduled"), 
    stringsAsFactors = FALSE
)
```

--- .class #id &twocol

## Our group sponsors

*** =left

```{r leftSponsor, echo = FALSE, cache = FALSE, fig.width = 6, fig.height = 6}
img <- readJPEG("./assets/img/RAlogo.jpg")
grid.raster(img)
```

*** =right

```{r rightSponsor, echo = FALSE, cache = FALSE, fig.width = 6, fig.height = 6}
img <- readPNG("./assets/img/MSlogo.png")
grid.raster(img)
```

--- .class #id 

## Number of group members

```{r groupStats, echo = FALSE, cache = FALSE, dpi = 72, fig.width = 14, fig.height = 7, dev.args = list(bg = 'transparent')}
## member stats
ggplot(data = memberStats) + 
    geom_line(aes(x = date, 
                  y = members, 
                  group = status, 
                  color = status)) + 
    scale_color_brewer(palette = "Set1") + 
    labs(list(x = "", 
              y = "Members", 
              color = "Member status")) + 
    geom_vline(aes(xintercept = as.numeric(date)), 
               data = milestones, 
               linetype = "dashed") + 
    geom_text(aes(x = date, 
                  y = 100, 
                  label = event), 
              data = milestones, 
              angle = 90, 
              vjust = 1, 
              hjust = 1, 
              size = 4) + 
    geom_point(aes(x = date, 
                   y = members), 
               data = maxMembers, 
               size = 3) + 
    theme_bw(base_size = 25) + 
    theme(panel.border = element_blank(), 
          plot.background = element_rect(fill = "transparent", 
                                         color = NA), 
          legend.key = element_rect(color = NA), 
          legend.key.size = unit(2, "lines"))
```

--- .class #id 

## Schedule for today

Time|What's happening
-------|-------
19:00|doors open
19:15|Konstantin Greger ([@kogreger](https://twitter.com/kogreger)): "Welcome address and brief introduction"
19:20|Berry Boessenkool ([@berryboessenkoo](https://twitter.com/berryboessenkoo)): TBA
19:35|Rick Scavetta ([@Rick_Scavetta](https://twitter.com/rick_scavetta)): "Some New Data Vis Tools in R - visR! 2015""
19:50|Andrew Dolman: "New R Engines and Interpreters""
20:05|Konstantin Greger ([@kogreger](https://twitter.com/kogreger)): "Spatial Analysis in R"
20:05|Michael Rustler: "Creating a Crowd Based Central Knowledge Hub for Reproducible Research with R"
afterwards|socializing & networking
22:00|doors close
